---
title: "My R Markdown Primer"
author: "Rayhan Khan"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

R Markdown is a file format that allows users to combine writing and R code in one document. It helps create reports where the code and results are shown together.

# Narrative Text

This is an example of writing normal text inside an R Markdown file. I can use **bold**, *italic*, and other formatting. R Markdown makes it easier to explain analysis while showing the actual code and output in the same report.

# Math Example

Inline math: $\alpha + \beta = \gamma$

Displayed math:

$$
\bar{x} = \frac{1}{n}\sum_{i=1}^{n} x_i
$$

# Code Example 1

```{r}
summary(mtcars)
```

# Code Example 2

```{r}
hist(mtcars$mpg,
     main = "Distribution of Miles Per Gallon",
     xlab = "MPG",
     col = "lightblue")
```

# Conclusion

Using R Markdown was different from writing a plain report because it combines explanation and code in one file. I found it helpful because I could write about the analysis and immediately include the output below it. This makes the document more organized and reproducible.

One challenge was understanding the difference between the .Rmd file and the final output, but after knitting the document it became clearer. Overall, R Markdown is a useful tool for combining data analysis and written explanation in a single report.